Computer-Assisted Analysis of the \\ Anderson-Hájek Ontological Controversy

### 2015-07-13 Papers/InProgress/HajekAndersonControversy/main.tex
Remove dead code
Ommit authors for double blind review

%----------AUTHOR 1
\author[Benzm\"uller]{C. Benzm\"uller}

\address{%
Dep.~of Mathematics and Computer Science, Freie Universit\"at Berlin, Germany
}
\email{c.benzmueller@fu-berlin.com}

\thanks{This work was supported by German National Research Foundation (DFG) under
 grants BE 2501/9-1 and BE 2501/11-1.}

%----------Author 2
\author[Weber]{L. Weber}
\address{
Dep.~of Mathematics and Computer Science, Freie Universit\"at Berlin, Germany
}
\email{leon.weber@fu-berlin.de}

%----------Author 3
\author[Woltzenlogel-Paleo]{B. Woltzenlogel Paleo}
\address{
Room HA0402, Favoritenstra{\ss}e 9, 1040 Wien, Austria
}
\email{bruno.wp@gmail.com}

@@

\newpage
\vskip 8em

\section{Summary}

\newcommand{\R}{Red.}
\newcommand{\S}{Sup.}
\newcommand{\P}{Prov.}
\newcommand{\CS}{Countersat.}
\newcommand{\U}{--}

\begin{tabular}{lccc}
Proof               & A4 & H:A4 & A5 & A5' & H:A5 & T3 & T3'  &  MC \\
\hline
Scott (const)       &
Scott (var)
Anderson (const)    &     &
Anderson (var)
\AOE
\AOEH
\AOEHH
\AOEHHH
\end{tabular}

\end{appendix}

>>>>

% %----------AUTHOR 1
% \author[Benzm\"uller]{C. Benzm\"uller}

% \address{%
% Dep.~of Mathematics and Computer Science, Freie Universit\"at Berlin, Germany
% }
% \email{c.benzmueller@fu-berlin.com}

% \thanks{This work was supported by German National Research Foundation (DFG) under
%  grants BE 2501/9-1 and BE 2501/11-1.}

% %----------Author 2
% \author[Weber]{L. Weber}
% \address{
% Dep.~of Mathematics and Computer Science, Freie Universit\"at Berlin, Germany
% }
% \email{leon.weber@fu-berlin.de}

% %----------Author 3
% \author[Woltzenlogel-Paleo]{B. Woltzenlogel Paleo}
% \address{
% Room HA0402, Favoritenstra{\ss}e 9, 1040 Wien, Austria
% }
% \email{bruno.wp@gmail.com}

@@
